---
title: "PSATA131-HW2"
author: "Yifan Xu"
date: "2022-10-17"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(tidymodels) 
library(ISLR)
library(ggplot2)
library(corrplot)
library(ggthemes)
library(yardstick)
tidymodels_prefer()
set.seed(100)
```

```{r}
abalone <- read.csv("abalone.csv")
head(abalone)
```

Q1

```{r}
# Add age column to the abalone with "rings" + 1.5
abalone["age"] <- abalone["rings"]+1.5
# To assess the distribution of age, we can use histogram to check
abalone %>% ggplot(aes(age))+geom_histogram(bins=30)

```

According to the plot, we can conclude that the distribution of age relatively follows the normal distribution with mean at about 10-12, but it is slightly skewed to the right. The majority of data locates between 4 and 17, however, there exist some extreme outliers around 25 to 32.


Q2


```{r}
abalone_split <- initial_split(abalone,prop=0.80,strata = age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```

Q3

```{r}
abalone_train_without_rings <- abalone_train %>% select(-rings)
abalone_recipe <- recipe(age ~ ., data = abalone_train_without_rings) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms= ~ starts_with("type"):shucked_weight+
                  longest_shell:diameter+
                  shucked_weight:shell_weight) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
abalone_recipe
```


We can’t use rings to predict age, because the age column is just the linear transformation of the rings column, they have exactly the same trend and distribution with shift. Thherefore, rings cannot be used to predict age.

Q4

```{r}
 lm_model<-linear_reg() %>%
  set_engine("lm")
```



Q5

```{r}
lm_wflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(abalone_recipe)
```


Q6

```{r}
lm_fit <- fit(lm_wflow,abalone_train %>% select(-rings))
female_pred <- data.frame(type = "F", longest_shell = 0.50,
                          diameter = 0.10, height = 0.30,
                          whole_weight = 4, shucked_weight = 1,
                          viscera_weight = 2, shell_weight = 1)
predict(lm_fit, new_data = female_pred)
```
```{r}
lm_fit %>%
# This returns the parsnip object: 
  extract_fit_parsnip() %>%
# Now tidy the linear model object:
  tidy()
```

Q7

```{r}
abalone_train_res <- predict(lm_fit, new_data = abalone_train_without_rings %>% select(-age))
abalone_train_res <- bind_cols(abalone_train_res, abalone_train_without_rings %>% select(age))
abalone_train_res %>%
  head()
```

```{r}
abalone_metrics<-metric_set(rmse,rsq,mae)
abalone_metrics(abalone_train_res, truth=age,
                estimate=.pred)
```
We get approximate 0.5543753	 for R squared value which indicates that 55.437525% of the data fit the regression model.

